{\vspace{-2cm}}Temporal Congestion Analysis and Predictive Modeling of Ride-Hailing Trips in NYC Using High-Volume FHV Data

### 2025-04-22 paper.tex
chore: Draft paper.

>>>>

\subsection{Limitations and Challenges}
While this proposed methodology uses scalable technologies and sound modeling techniques, there are several limitations to consider. First, the dataset does not include contextual features, such as weather conditions, traffic incidents, or public transit disruptions, which can influence congestion and travel duration. Second, logistic regression assumes linearity between predictors and the log-odds of the outcome, which may oversimplify the relationship between variables such as time of day or provider and congestion. Third, the use of static, historical data limits the system's ability to capture sudden shifts in rider behavior, service availability, or city policy. Additionally, any real-time extension would depend on reliable APIs or streaming data access from service providers, which may not be publicly available. Finally, ensuring fairness and mitigating bias in modeling outcomes will be essential, especially when interpreting differences between providers or geographic regions.
